Efficiently stable presentations from error-correcting codes

### 2023-10-04 efficient_stability.tex
Updates from Overleaf

Now, for every $v\in \field^{k+1}$, we have
1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq |1-(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq \Vert \Id_\mM(\Id_\infty-B_1A_1)e_v\otimes e_1\Vert_2^2.
On the other hand, since $B_1A_1$ is a contraction, 

@@

    1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2
    &\geq \Vert B_1A_1 e_v\otimes e_1\Vert_2^2-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\\
    &=\sum_{(v',j')\neq (v,1)}|(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2\\
    &\geq \Vert (\Id_\infty-\Id_\mM)B_1A_1 e_v\otimes e_1\Vert_2^2.

@@

Therefore, by averaging the combined inequalities over $v\in \field^{k+1}$, we get
\Vert (\Id_\infty -\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_1A_1)\Id_\mM\Vert_\tau^2=\Vert A_1-\Id_\mM B_1\Id_\mM\Vert_\tau^2.
\begin{comment}
=\frac{1}{2^{k+1}}\sum_{\substack{v\in \field^{k+1}}} \sum_{\substack{v'\in \field^{k+1}\\ j'\neq 1}} \vert (e_{v'}\otimes e_j)^*B_1 e_v\otimes e_1\vert^2.
\end{comment}
Plugging all of this back to $(\spadesuit)$, we get

@@

    (\sqrt{2}-\eps)^2&\leq (\spadesuit)^2\\
    &\leq 8\Vert(A_1-B_1)\Id_\mM\Vert^2+8\Vert(A_2-B_2)\Id_\mM\Vert^2\\
    &\leq 16 \Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert^2+16 \Vert \Id_\mM (A_2-B_2)\Id_\mM\Vert^2\\
    &\leq 16k \eps,
and since we assumed $\eps<\sqrt{2}-1$ we deduce that 
\eps>\frac{1}{16k}.
This finishes the proof.

>>>>

\mnote{ By definition, 

@@

    \Vert(\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=\diamondsuit

@@

but since $A_1$ permutes the basis of $\{e_v\otimes e_1\}$, we have

@@

    \diamondsuit=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2.
\end{align*}}

Now, for every $v\in \field^{k+1}$, we have
\[
1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq |1-(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq \Vert \Id_\mM(\Id_\infty-B_1A_1)e_v\otimes e_1\Vert_2^2.
\]
On the other hand, since $B_1A_1$ is a contraction, 
\begin{align*}
    1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2
    &\geq \Vert B_1A_1 e_v\otimes e_1\Vert_2^2-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\\
    &=\sum_{(v',j')\neq (v,1)}|(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2\\
    &\geq \Vert (\Id_\infty-\Id_\mM)B_1A_1 e_v\otimes e_1\Vert_2^2.
\end{align*}
Therefore, by averaging the combined inequalities over $v\in \field^{k+1}$, we get
\[
\Vert (\Id_\infty -\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_1A_1)\Id_\mM\Vert_\tau^2=\Vert A_1-\Id_\mM B_1\Id_\mM\Vert_\tau^2.
\]
\begin{comment}
=\frac{1}{2^{k+1}}\sum_{\substack{v\in \field^{k+1}}} \sum_{\substack{v'\in \field^{k+1}\\ j'\neq 1}} \vert (e_{v'}\otimes e_j)^*B_1 e_v\otimes e_1\vert^2.
\end{comment}
Plugging all of this back to $(\spadesuit)$, we get
\begin{align*}
    (\sqrt{2}-\eps)^2&\leq (\spadesuit)^2\\
    &\leq 8\Vert(A_1-B_1)\Id_\mM\Vert^2+8\Vert(A_2-B_2)\Id_\mM\Vert^2\\
    &\leq 16 \Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert^2+16 \Vert \Id_\mM (A_2-B_2)\Id_\mM\Vert^2\\
    &\leq 16k \eps,
\end{align*}
and since we assumed $\eps<\sqrt{2}-1$ we deduce that 
\[
\eps>\frac{1}{16k}.
\]
This finishes the proof.
\end{proof}
